Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Add STEM percentage

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. About one-half of the participants were in STEM fields, the others were distributed relatively evenly between agriculture, business, and the social sciences. Students were evenly distributed by gender, and were between 18 and 24 years of age with only one exception. This is reasonably representative\footnote{\url{http://www.ir.iastate.edu/PDFfiles/2012-2013\%20Student\%20Profile.pdf}} of the university as a whole; in the fall 2012 semester, 23\% of students were associated with the college of engineering, 23\% were associated with the college of liberal arts and sciences, 23\% were associated with the college of human sciences, 12\% with the business school, and 14\% with the school of agriculture.

>>>>

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. \Sexpr{round(sum(ans.summary$stem)/nrow(ans.summary)*100)}\% of the participants were in STEM fields, the others were distributed relatively evenly between agriculture, business, and the social sciences. Students were evenly distributed by gender, and were between 18 and 24 years of age with only one exception. This is reasonably representative\footnote{\url{http://www.ir.iastate.edu/PDFfiles/2012-2013\%20Student\%20Profile.pdf}} of the university as a whole; in the fall 2012 semester, 23\% of students were associated with the college of engineering, 23\% were associated with the college of liberal arts and sciences, 23\% were associated with the college of human sciences, 12\% with the business school, and 14\% with the school of agriculture.
